---
title: "Location of Boojum Burrito Bars in Ireland"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(data.table)
library(dplyr)
library(leaflet)
```

```{r, echo=FALSE}
coords <- fread("coords.csv")
```

### **NOTE:** Locations are correct as of 19th September 2018

## Why this Map?

Many of the people of Ireland (both north and south of the border) love Mexican food. There are many food outlets that now offer a burrito bar alongside traditional offerings such as an Ulster/Irish breakfast, sandwiches and other hot foods. One such place that is popular is a chain of burrito bars called Boojum.
 
## What is a Boojum?

Boojum opened in 2007 as a casual Mexican food bar. They have an award winning yet simple menu. Further information can be found on their own website at <http://www.boojummex.com>. Boojum have 17 stores accross Ireland in Belfast (5), Dublin (9), Cork, Galway and Limerick.

## Interactive Map of Store Locations

Click on a icon to see its address.

```{r, echo=FALSE}
bjicon <- makeIcon(iconUrl = "https://pbs.twimg.com/profile_images/1026414504983371776/kSOIQ-vX_400x400.jpg",
                  iconWidth = 30,
                  iconHeight = 30
                  )

map2 <- leaflet() %>%
     addTiles() %>%
     addMarkers(.,
                lat = coords$lat,
                lng = coords$long,
                clusterOptions = markerClusterOptions(),
                icon = bjicon,
                popup = coords$location
                )

map2
```

## Location List

```{r, echo=FALSE}
colnames(coords) <- c("City","Address","Latitude","Longitude")
coords %>% arrange(., City, desc(Latitude), Longitude) %>% kable()
```

## Disclaimer

**This website is for a project about building an interactive map using the leaflet package from R. The author has no connection with Boojum, the spread and number of the locations just make a good practice project. Other burrito outlets in Ireland (i.e. Northern Ireland and the Republic of Ireland) are availible.**
